---
title: "gpelose_FinalHomeworkCode_04"
author: "Greg Pelose"
date: "10/27/2019"
output: html_document
---

[1] Write a simple R function, Z.prop.test(), that can perform one- or two-sample Z-tests for proportion data, using the following guidelines:

I am struggling on where to begin here, I will need to spend more time over tomorrow and sunday to try and figure this out.. 



[2] The dataset from Kamilar and Cooper has in it a large number of variables related to life history and body size. For this exercise, the end aim is to fit a simple linear regression model to predict longevity (MaxLongevity_m) measured in months from species’ brain size (Brain_Size_Species_Mean) measured in grams. Do the following for both  longevity~brain size and log(longevity)~log(brain size):

I will first install my packages.

```{r}
install.packages("ggplot2")
install.packages("curl")
```

I will then load these packages into my library

```{r}
library(ggplot2)
library(curl)
```

Now I will be loading my dataset

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

Success, remind to self to watch out for the NA values. 

```{r}
names(d)
```

```{r}
p <- plot(data = d, Brain_Size_Species_Mean ~ MaxLongevity_m, col = "blue", main = "Brain Size against Longevity")
geom_line(p)
```

creating a Model 1 regression.

```{r}
m <- lm(Brain_Size_Species_Mean ~ MaxLongevity_m, data = d)
m
summary(m)
```

I got an adjusted R-squared number of 0.4887, this shows me that 48 percent of the variation in y is explained by x. This is not statistically significant but this does show a slight significance. 

```{r}
plot(m)
```

```{r}
g <- ggplot(data = d, aes(x = MaxLongevity_m, y = Brain_Size_Species_Mean, main = "Brain Size vs. Longevity"))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g
```

The plot(m) graphs all look quite disorganized, by the scatterplot that I created in ggplot looks slightly normal in the beginning but has many more outliers as you increase both brian size and 
***
Next I will be taking the log of each of the variables to try and make the data come out better. 

```{r}
d$logMaxLongevity_m <- log(d$MaxLongevity_m)
d$logBrain_Size_Species_Mean <- log(d$Brain_Size_Species_Mean)
plot(data = d, logMaxLongevity_m ~ logBrain_Size_Species_Mean)
model <- lm(data = d, logMaxLongevity_m ~ logBrain_Size_Species_Mean)
summary(model)
plot(model)
```

Above, I added all of the code into one line of code. The r squared is .5751, this is a better number than before. 

```{r}
qqPlot(model$residuals)
```

The qqplot shows that everything is inside of the confidence intervals.
***
NEXT SECTION
***
Identify and interpret the point estimate of the slope (β1), as well as the outcome of the test associated with the hypotheses H0: β1 = 0; HA: β1 ≠ 0.

```{r}
b <- d$logBrain_Size_Species_Mean
l <- d$logMaxLongevity_m
slope <- lm(l ~ b)
slope
```

This function above shows me the slope (B1), this value is .2341.

```{r}
m <- lm(data = d, logMaxLongevity_m ~ logBrain_Size_Species_Mean)
ci <- confint(m, level = 0.90)  # using the results of lm()
ci

```






